Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures. Consider the collection
of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
$\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
and vice versa. In another word, quantum IVPMs with $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures where
Gleason's theorem can apply.

$\mathscr{I}_{\infty}$ is one extreme case of quantum IVPM; another
extreme case happens when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
can be applied and will be explained in the next paragraph.

@@

Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
definition of \emph{core} relative to a sub-event space~$\events'\subseteq\events$
as follow.
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{B}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
Although the elements of a core are density matrices, we may just
use the state vectors for pure states if it is clear in the context.
For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
where $\circ$ denote function composition.

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
to $\events_{0}$ where every projectors are mutually commutative.
Recall commutative sub-event space reduces quantum IVPMs to classical
IVPMs. In general, we haven't found any classical IVPM has a non-empty
core, and Shapley has proved that a good enough classical IVPM always
has a non-empty core.

@@

>>>>

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures. Consider the collection
of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
given a quantum real-valued probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
$\bar{\mu}(P)=\iota_{\infty}\left(\mu(P)\right)$ is a quantum IVPM,
and vice versa. In another word, quantum IVPMs mapping to $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures where
Gleason's theorem can apply.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
can be applied and will be explained in the next paragraph.

@@

Given a quantum IVPM~$\bar{\mu}$, the preceding idea motivates the
definition of \emph{core} relative to a sub-event space~$\events'\subseteq\events$
as follow.
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{B}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
Although the elements of a core are density matrices, we may just
use the state vectors for pure states if it is clear according to
the context. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \ket{\ps}\right\} $
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
where $\circ$ denote function composition.

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
to $\events_{0}$ which is commutative. Recall a commutative sub-event
space reduces quantum IVPMs to classical IVPMs. In general, we haven't
found any classical IVPM has an empty core, and Shapley proved that
a good enough classical IVPM always has a non-empty core.

@@

In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
when $d\ge3$.
